---
title: "**Michelin Stars and Price**"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r echo = FALSE, message = FALSE, warning=FALSE}
library(tidyverse)
data = read.csv("./data/michelin_data.csv")


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r echo = FALSE, message = FALSE, warning=FALSE}
data = data %>%
  mutate(
    cuisine_new = fct_collapse(cuisine,
                   American = c("American", "Californian"), 
                   Australian = c("Australian"),
                   Other_Asian = c("Asian", "Asian contemporary", "Asian influences", "Peranakan"),
                   Chinese = c("Cantonese", "Hang Zhou", "Sichuan", "Sichuan-Huai Yang", "Cantonese Roast Meats", "Fujian", "Hunanese and Sichuan", "Chinese", "Shanghainese", "Taiwanese", "Dim Sum", "Taizhou", "Noodles and congee"), 
                   French = c("Classic French", "French contemporary", "Creative French", "French", "Modern French"),
                   British = c("Creative British", "Traditional British", "Modern British"), 
                   Other_European = c("European", "European contemporary", "Austrian", "Danish", "Finnish"),
                   Meats = c("Meats and grills", "Barbecue"),
                   Modern = c("modern", "Contemporary", "creative", "Fusion", "Modern cuisine", "Creative", "Gastropub", "Innovative"), 
                   Other = c("International", "Street Food", "Temple cuisine", "Seafood", "Vegetarian", "Classic cuisine", "Market cuisine", "Regional cuisine", "Steakhouse", "Moroccan"), 
                   Japanese = c("Japanese contemporary", "Sushi", "Teppanyaki", "Japanese"),
                   Scandinavian = c("Scandinavian"),
                   Italian = c("Italian", "Italian contemporary"),
                   Korean = c("Korean", "Korean contemporary"), 
                   Mediterranean = c("Mediterranean", "Mediterranean cuisine"),
                   Thai = c("Thai", "Southern Thai", "Thai Contemporary"), 
                   Indian = c("Indian"), 
                   Spanish = c("Spanish"), 
                   Mexican = c("Mexican"))
  )
```

```{r echo = FALSE, message = FALSE, warning=FALSE}
data = data %>%
  mutate(
    Stars = recode(star, "one" = "1", "two" = "2", "three" = "3"))
```

&nbsp;

## Price Distribution For Each Star Groups' Restaurants

<br>To learn more about Michelin restaurants, we decided to investigate how is the star rating associated with restaurant's price level. 

<br>

```{r echo = FALSE, message = FALSE, warning=FALSE}
data %>%
  mutate(
    price = as.numeric(price)) %>%
  drop_na(Stars, price) %>%
  ggplot(aes(x = Stars, y = price, fill = Stars))+
    geom_violin(alpha = 0.5) +
  labs(
    title = "Price Distribution for Each Star Groups",
    x = "Stars", 
    y = "Price"
  )
```

<br>Looking at the distribution of price separately for each star rating groups, the violin graph shows that 1-star restaurants have a spread out distribution of price levels, while 2-star restaurants and 3-star restaurants have a higher distribution of price at 4 level and 5 level. This could potentially suggest that higher stared restaurants have higher price levels. 

&nbsp;

## Average Price Level For Each Star Rating Groups

<br>We can further confirm our guess by plotting the average price level for each star groups: 

```{r echo = FALSE, message = FALSE, warning=FALSE}
data2 = data %>%
  mutate(
    price = as.numeric(price)
  ) %>%
  drop_na(price, Stars) %>%
  group_by(Stars) %>%
  summarize(avg_price = mean(price)) 

data2 %>%
  ggplot(aes(x = Stars, y = avg_price, color = Stars, group = 1)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Average Price for Each Star Groups", 
    x = "Stars", 
    y = "Average price"
  )
```

<br>The plot shows that there is a large jump on average price between 2-star restaurants and 1-star restaurants. The average price level keeps increasing from 2-star to 3-star restaurants with a smaller increment. Star level positively correlates with price level, which is consistent what we would normally expected that restaurants with higher star ratings have higher price level. 

&nbsp;

## Discussion 

<br>Since price information in the dataset is categorical data that 5 different price levels were provided as number of $ signs, we would loose a lot of information by treating is as a continuous variable and thus poses limitations to our analysis. 