---
title: "**Cuisine Type and Restaurant Price**"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning =FALSE, include=FALSE}

library(tidyverse)
library(readxl)
library(ggplot2)
library(plotly)

final = read_csv("./data/michelin_data.csv")

```

<br>Michelin starts are awarded to restaurants judged to be of a particularly high standard. Eateries that make the grade can be awarded on, two three stars. But what about the prices? Are certain cuisine associated with higher prices? In addition, do the prices varies by the continent?

&nbsp;

## Cusine Type Overview

<br>Within our existing dataset, let's first take a look at the number of cuisine types in our Michelin restaurant. We can see that among all Michelin Restaurant, **Modern Cuisine, Contemporary, Japanese, Creative, Cantonese, Modern British and French** are at the top of the list. 

```{r message=FALSE, warning =FALSE}
cuisine_type = final %>% 
   group_by(cuisine) %>% 
   summarise(count = n())  %>% 
    mutate(cuisine = fct_reorder(cuisine, count)) 

cuisine_plot = 
  cuisine_type %>%
  ggplot(aes(x = cuisine, y = count)) +
  geom_point(color = "red") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("Types of Cuisine Among All Micheline Restaurants") +
  xlab("Cuisine Type") +
  ylab("Number of Restaurant") 

ggplotly(cuisine_plot)

```



<br>Now let's take a look at the how these restaurants distributed around the world. 

```{r message=FALSE, warning =FALSE}
country = final %>% 
   group_by(continent) %>% 
   summarise(continent_count = n()) 
   

knitr::kable(country)
```


```{r message=FALSE, warning =FALSE, echo = FALSE}
final_clean = final %>%
   mutate(cuisine_cat = fct_collapse(cuisine,
                   American = c("American", "Californian"), 
                   Australian = c("Australian"),
                   Other_Asian = c("Asian", "Asian contemporary", "Asian influences", "Peranakan"),
                   Chinese = c("Cantonese", "Hang Zhou", "Sichuan", "Sichuan-Huai Yang", "Cantonese Roast Meats", "Fujian", "Hunanese and Sichuan", "Chinese", "Shanghainese", "Taiwanese", "Dim Sum", "Taizhou", "Noodles and congee"), 
                   French = c("Classic French", "French contemporary", "Creative French", "French", "Modern French"),
                   British = c("Creative British", "Traditional British", "Modern British"), 
                   Other_European = c("European", "European contemporary", "Austrian", "Danish", "Finnish"),
                   Meats = c("Meats and grills", "Barbecue"),
                   Modern = c("modern", "Contemporary", "creative", "Fusion", "Modern cuisine", "Creative", "Gastropub", "Innovative"), 
                   Other = c("International", "Street Food", "Temple cuisine", "Seafood", "Vegetarian", "Classic cuisine", "Market cuisine", "Regional cuisine", "Steakhouse", "Moroccan"), 
                   Japanese = c("Japanese contemporary", "Sushi", "Teppanyaki", "Japanese"),
                   Scandinavian = c("Scandinavian"),
                   Italian = c("Italian", "Italian contemporary"),
                   Korean = c("Korean", "Korean contemporary"), 
                   Mediterranean = c("Mediterranean", "Mediterranean cuisine"),
                   Thai = c("Thai", "Southern Thai", "Thai Contemporary"), 
                   Indian = c("Indian"), 
                   Spanish = c("Spanish"), 
                   Mexican = c("Mexican"))
  ) %>%
          drop_na(price, continent)  
```

<br>We have categorized our cuisine types into smaller group, like Modern French and French are both categorized into the French Cuisine Type so we do not have to many duplicate cuisine types in our analysis. 

<br>Now let's take a look at the Number of Restaurants in each Cuisine Type by Michelin Star. You can see some really interesting points here, Modern Cuisine Type not only have the largest number in restaurants, it also have the largest number of one star Restaurants in the world!

```{r message=FALSE, warning =FALSE}
cuisine_type = final_clean %>% 
   group_by(cuisine_cat,star) %>% 
   summarise(count = n())  %>% 
    mutate(cuisine_cat = fct_reorder(cuisine_cat, count)) 

cuisine_plot = 
  cuisine_type %>%
  ggplot(aes(x = cuisine_cat, y = count, fill=star)) +
  geom_bar(stat = 'identity',position = 'dodge') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("Number of Restaurants in each Cuisine Type by Michelin Star") +
  xlab("Cuisine Type") +
  ylab("Number of Restaurant")

cuisine_plot

```



&nbsp;

## Cuisine Type and Price

<br>Now let's take a look at the cuisine type and their price around the world. We can clearly see that some types of cuisine are usually priced higher than the others. For instance, **Mediterranean cuisines (4.00) and Japanese cuisine (3.96)** are usually the most expensive, while **Australian (1.50) and Cantonese cuisines (2.03)** typically have lower prices.

```{r message=FALSE, warning =FALSE}
world_plot = final_clean %>%
    mutate(cuisine = factor(cuisine_cat)) %>%
    group_by(cuisine)%>%
    summarise(mean_price = mean(price))  %>%
  ggplot(aes(x = cuisine, y = mean_price, color = "red")) + 
  geom_point(color = "darkgreen")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("Cuisine types and their average price around the World") +
  xlab("Cuisine Type") +
  ylab("Mean Price of this Cuisine Type") 

ggplotly(world_plot)
```




```{r message=FALSE, warning =FALSE, echo = FALSE}
final_asia = final_clean %>%
   subset(continent == "Asia")
```

```{r message=FALSE, warning =FALSE, echo = FALSE}
final_europe = final_clean %>%
  subset(continent == "Europe")
```

```{r message=FALSE, warning =FALSE, echo = FALSE}
final_na= final_clean %>%
  subset(continent == "North America")
```

```{r message=FALSE, warning =FALSE, echo = FALSE}
final_sa= final_clean %>%
  subset(continent == "South America")
```

&nbsp;

## Cuisine Type and Price by Continent

&nbsp; 

### _Asia_

Let's first explore the relationship between cuisine type and its price in Asia. We can see that in Asia, the most expensive cuisine type is Japanese while cheapest cuisine type is Indian. 


```{r message=FALSE, warning =FALSE}
asia_plot = final_asia %>%
    mutate(cuisine_cat = factor(cuisine_cat)) %>%
    group_by(cuisine_cat)%>%
    summarise(mean_price = mean(price))  %>%
  ggplot(aes(x = cuisine_cat, y = mean_price)) + 
  geom_point(color = "red")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("Asia: The Cuisine type and their average prices") +
  xlab("Cuisine Type") +
  ylab("Mean Price of this Cuisine Type") 

ggplotly(asia_plot)

```



&nbsp;

### _Europe_ 

In Europe, the most expensive cuisine type is **Mediterranean** which also aligns with our overall plot before stratifying with continents. The cheapest cuisine types in **Europe are Thai and Italian**, which is really unexpected. 

```{r message=FALSE, warning =FALSE}
europe_plot = final_europe %>%
    mutate(cuisine_cat = factor(cuisine_cat)) %>%
    group_by(cuisine_cat)%>%
    summarise(mean_price = mean(price))  %>%
  ggplot(aes(x = cuisine_cat, y = mean_price)) + 
  geom_point(color = "purple")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("Europe: Cuisine types and their average prices") +
  xlab("Cuisine Type") +
  ylab("Mean Price of this Cuisine Type") 

ggplotly(europe_plot)
```



&nbsp;

### _North America_ 

In North America, the most expensive cuisine types are **Scandinavian and other_European**, the cheapest type is **Chinese**. 
```{r message=FALSE, warning = FALSE}
na_plot = final_na %>%
    mutate(cuisine_cat = factor(cuisine_cat)) %>%
    group_by(cuisine_cat)%>%
    summarise(mean_price = mean(price))  %>%
  ggplot(aes(x = cuisine_cat, y = mean_price)) + 
  geom_point(color = "darkblue")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("North America: Cuisine types and their average prices") +
  xlab("Cuisine Type") +
  ylab("Mean Price of this Cuisine Type") 

ggplotly(na_plot)
```



&nbsp;

### _South America_ 

In South America, most of the cuisine types are expensive, while only **Japanese** has a relatively lower prices, which is 4.67. However, please note that in South America we have very limited data so this is not a representative measure of the cuisine types and prices in South America. 
```{r message=FALSE, warning =FALSE}
sa_plot = final_sa %>%
    mutate(cuisine_cat = factor(cuisine_cat)) %>%
    group_by(cuisine_cat)%>%
    summarise(mean_price = mean(price))  %>%
  ggplot(aes(x = cuisine_cat, y = mean_price)) + 
  geom_point(color = "pink")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 0.5)) + 
  ggtitle("South America: The relationship between cuisine types and their prices") +
  xlab("Cuisine Type") +
  ylab("Mean Price of this Cuisine Type") 

ggplotly(sa_plot)
```



